Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.
[ paper ] fixed typos in canonicalize.
Cosmetic changes.

The positive literal $ℓ$ must occur in
the formula from the first derivation and the
negative literal $¬ ℓ$ must occur in the formula from the second derivation,
see the pattern of the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.

@@

Using reordering after
applying a customized version of the resolution theorem defined
in~\eqref{eq:rsol} we get the expect result.

@@

\begin{mainth}
  \label{thm:resolve}
  Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$, where
  \begin{equation}
  \begin{split}
  \label{eq:resolve}
    &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
    &\fresolve~φ₁~φ₂~ℓ~ψ =
      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
  \end{split}
  \end{equation}
\end{mainth}

>>>>

The positive literal~$ℓ$ must occur in the formula from the first
derivation and the negative literal~$¬ ℓ$ must occur in the formula
from the second derivation, see the pattern of the \emph{resolve} rule
in Fig.~\ref{fig:metis-inferences}.

@@

Using reordering after
applying a customized version of the resolution theorem defined
in~\eqref{eq:rsol} we get the expected result.

@@

\begin{mainth}
  \label{thm:resolve}
  Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$ where,
  \begin{equation}
  \begin{split}
  \label{eq:resolve}
    &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
    &\fresolve~φ₁~φ₂~ℓ~ψ =
      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
  \end{split}
  \end{equation}
\end{mainth}
